Capturing the geometric structure of our experiences and how we remember them

### 2018-07-25 main.tex
methods edits

\subsection{Participants and Experimental Design}
Participants ($n$=17) viewed \textit{A Study in Pink}, a 50 minute episode of the BBC series, \textit{Sherlock}. Immediately upon completion of the video, participants were instructed to (verbally) recount the events in the video in their original order and in as much detail as possible. During the entire experiment, participants were in an fMRI scanner.  However, only the behavioral data (e.g. the recall transcripts) were used in this paper. For comprehensive details of the experimental procedures, please refer to \cite{ChenEtal17}.

\subsubsection{Fitting the topic model to the video text and recall transcripts}
A topic model was used to estimate the most likely mixture of topics for a given sample of text. First, the video was manually segmented into 1000 scenes, and a collection of descriptive features was manually transcribed. For each scene, we considered the following features: scene details (i.e. a sentence or two describing what happened in that scene, space (indoor or outdoor), name of all the characters in the scene, name of the character in focus, name of the character speaking, location, camera angle, music presence, and words on the screen. We concatenated the text for all of these features within each segment, creating a 'bag of words' describing each scene. We then transformed the text descriptions into overlapping windows of 50 scene segments. For example, the first text sample comprised the text from the first 50 segments, the second comprised the text from n+1:n+51, and so on. We trained our model using these overlapping text samples using scikit-learn's (version 0.19.1) `CountVectorizer' and `LatentDirichletAllocation' classes.  First, the text was transformed into a vector of word counts (default parameters). This gave a word count vector for each scene in the video.  Then, the word count vectors were used to fit a topic model (\# of topics=100, method=batch). We transformed the text descriptions using the model resulting in a scenes (1000) by topics (100) matrix. The scene descriptions often spanned multiple timepoints (i.e. TRs). To account for this, we expanded the video model by copying the rows of the model for as many timepoints that the scene description spanned. After this expansion, the shape of the model was the length of the duration of the video (1976 TRs).

@@

@@

Our metric for choosing the `best fitting' HMM was to choose the model with the $k$ value that maximized the ratio of the average `within-event' correlation values (i.e. the correlation values for blocks of consecutive timepoints the model identified as one event) and the average `across-event' correlation (i.e. the rest of the correlation values). Additionally, we included a penalty parameter that was proportional to the smoothing of the model that preferred models with smaller $k$ values. We chose $k$ values separately for the video model and for each recall model.  Then, using the best $k$ values, We fit a separate HMM for each topic model. Finally, we averaged over timepoints identified to be in the same event resulting in a $k$ events by 100 topics matrix for the video model and each of the recall models.
%
\subsubsection{Matching recall events to video events}
To figure out which video event each recall event referred to, we correlated the video events model and each recall events model. This resulted in a video events (34) by recall events (8-27) correlation matrix (for each participant) which contains the similarity between each video event and each recall event.  To find the most likely video event that a given recall event referred to, we computed the argmax over the columns of this matrix.  The result was a list of video event indices for each participant. These indices are analogous to the values found in a ``recall matrix'' from a free recall list learning experiment, but represent the recall of particular events (instead of words, for example).
%
\subsubsection{Characterizing memory performance using traditional approaches}

@@

%NOTE: Potentially more stringent test? One idea I had was for each grid point, find the number of line segments that passed through it, and then randomly sample that number from all line segments to build a null distribution for that point. Compute p value from this distribution.

>>>>

\subsection{Participants and Experimental Design}
Participants ($n$=17) viewed \textit{A Study in Pink}, a 50 minute episode of the BBC series, \textit{Sherlock}. Immediately upon completion of the video, participants were instructed to (verbally) recount the events in the video in their original order and in as much detail as possible. During the entire experiment, participants were in an fMRI scanner. For comprehensive details of the experimental procedures, please refer to \cite{ChenEtal17}.
%NOTE: is this sufficient or should i provide more detail?

\subsubsection{Fitting the topic model to the video text and recall transcripts}
A topic model was used to estimate the most likely mixture of topics for a given sample of text. First, the video was manually segmented into 1000 scenes, and a collection of descriptive features was manually transcribed. For each scene, we considered the following features: scene details (i.e. a sentence or two describing what happened in that scene, space (indoor or outdoor), name of all the characters in the scene, name of the character in focus, name of the character speaking, location, camera angle, music presence, and words on the screen. We concatenated the text for all of these features within each segment, creating a 'bag of words' describing each scene. We then transformed the text descriptions into overlapping windows of 50 scene segments. For example, the first text sample comprised the text from the first 50 segments, the second comprised the text from n+1:n+51, and so on. We trained our model using these overlapping text samples using scikit-learn's (version 0.19.1) `CountVectorizer' and `LatentDirichletAllocation' classes.  First, the text was transformed into a vector of word counts (default parameters). This gave a word count vector for each scene in the video.  Then, the word count vectors were used to fit a topic model (topics=100, method=batch). We transformed the text descriptions using the model resulting in a scenes (1000) by topics (100) matrix. The scene descriptions often spanned multiple timepoints (i.e. TRs). To account for this, we expanded the video model by copying the rows of the model for as many timepoints that the scene description spanned. After this expansion, the shape of the model was the length of the duration of the video (1976 TRs).

@@

\subsubsection{Choosing topic model parameters}
There were 3 critical parameters related to fitting the topic model: 1) the number of topics, 2) the window size of text descriptions of the video used to fit the model, and 3) the window size of recall sentences used to transform the recall data.  To chose these parameter values, we performed a grid search where the range of possible parameter values was 1, 5, 10, 25, 50, 100, 200, and 500. Our optimization objective was defined as the correlation between the hand annotated memory performance and the root mean squared distance between the video model and the recall model before any further processing (e.g. hidden Markov modelling, averaging within event, etc). While many of the parameter combination elicited moderately high correlations, the best choice was 100 topics, 50 video segments and 10 recall sentences.

@@

Our metric for choosing the `best fitting' HMM was to choose the model with the $k$ value that maximized the ratio of the average `within-event' correlation values (i.e. the correlation values for blocks of consecutive timepoints the model identified as one event) and the average `across-event' correlation (i.e. the rest of the correlation values). Additionally, we included a penalty parameter that was proportional to the smoothing of the model that preferred models with smaller $k$ values. We chose $k$ values separately for the video model and for each recall model.  Then, using the best $k$ values, We fit a separate HMM for each topic model. Finally, we averaged over timepoints identified to be in the same event resulting in a events by topics matrix for the video model and each of the recall models.
%
\subsubsection{Matching recall events to video events}
To figure out which video event each recall event referred to, we correlated the video events model and each recall events model. This resulted in a video events (34) by recall events (8-27) correlation matrix (for each participant) which contains the similarity between each video event and each recall event.  To find the most likely video event that a given recall event referred to, we computed the argmax over the columns of this matrix.  The result was a list of video event indices for each participant. These indices are analogous to the values found in a ``recall matrix'' from a free recall list learning experiment, but represent the recall of particular events (instead of words, for example).
%
\subsubsection{Characterizing memory performance using traditional approaches}

@@
